\documentclass[12pt, letterpaper]{article}
\usepackage{SyllabusStyle}

\begin{document}
\begin{center}
	{\Large \textsc{Elementary Chemistry Lab}}
	
	CHEM 1115
\end{center}
\begin{center}
	{\large Spring 2021}
\end{center}
\begin{center}
	\rule{0.85\textwidth}{0.4pt}
	\begin{tabular}{llcll}
		\textbf{Instructor:} & Matthew Rowley & & \textbf{Office Hours:} & Daily 1:00 pm - 2:00 pm \\
		\textbf{Telephone:} & (435) 586-7875 & & \textbf{Office:} & SC-220 \\
		\textbf{Email:} & \multicolumn{3}{l}{matthewrowley$1$@suu.edu}\\
		\multicolumn{5}{c}{Please include the course number in the subject line of all correspondence.} 
	\end{tabular}
	\rule{0.85\textwidth}{0.4pt}
\end{center}

\section*{Tentative Schedule}
This class will meet in room 208 of the Skaggs Center for Health \& Molecular Sciences (SCA)
\begin{itemize}
	\item Section 03 will meet on Fridays from 8:00 am – 9:50 am
	\item Section 04 will meet on Tuesdays from 8:00 am – 9:50 am
	\item Section 06 will meet on Mondays from 10:00 am – 11:50 am
\end{itemize}

\paragraph*{Week 1: Jan. 11 -- Jan 15}~

All sections: -- \textbf{No Lab}

\paragraph{Week 2: Jan. 18 -- Jan 22}~ 

Sections 03 and 04: Check-in and Safety and Techniques

Section 06: \textbf{No Lab (Martin Luther King, Jr. Day)}

\paragraph{Week 3:  Jan. 25 -- Jan 29}~

Sections 03 and 04:  Density and Measurements

Section 06: Check-in and Safety and Techniques

\paragraph{Week 4: Feb. 1 -- Feb. 5}~

Sections 03 and 04: Atomic Identification

Section 06: Density and Measurements

\paragraph{Week 5: Feb. 8 -- Feb. 12}~

Sections 03 and 04:  Chemical Names and Structures (This lab will be done remotely)

Section 06: Atomic Identification

\paragraph{Week 6: Feb. 15 -- Feb. 19}~ 

Sections 03 and 04:  \textbf{No Lab}

Section 06: Chemical Names and Structures (This lab will be done remotely)

\paragraph{Week 7: Feb. 22 -- Feb. 26}~

All sections: Chemical Formulas

\paragraph{Week 8: Mar. 1 -- Mar. 5}~ 

All sections: \textbf{No Classes this week (Spring Break!)}

\paragraph{Week 9: Mar. 8 -- Mar. 12}~

All sections: Chemical Reactions

\paragraph{Week 10: Mar. 15 -- Mar. 19}~

All sections: Stoichiometry

\paragraph{Week 11: Mar. 22 -- Mar. 26}~

All sections: Chemical Equilibrium

\paragraph{Week 12: Mar. 29 -- Apr. 2}~ 

All sections: Collection of Hydrogen Gas

\paragraph{Week 13: Apr. 5 -- Apr. 9}~

All sections: Electrolytes

\paragraph{Week 14: Apr. 12 -- Apr. 16}~

All sections: Acid-Base Chemistry and Lab Checkout

\paragraph{Week 15: Apr. 19 -- Apr. 23}~

All sections: \textbf{Final Exam} (More details about the final will come)

\paragraph{Finals Week}~

All sections: No Final -- You took it last week!

\end{document}